Interval Probability for Fuzzy Quantum Theories

### 2016-05-14 prob.tex
prob.tex \subsection{Real-Valued Probability Spaces} Modify a little bit

The conventional definition of a probability
space~\cite{inun.425605319950101,GrahamKnuthPatashnik1994,rohatgi2011introduction}
builds upon the real numbers. In more detail, a probability space
consists of a \emph{sample space} $\Omega$, a space of
\emph{events}~$\events$, and a \emph{probability measure}~$\pmeas$
mapping events in $\events$ to the real interval $[0,1]$. In this
paper, we will only consider \emph{finite} sets of events: we
therefore restrict our attention to non-empty finite sets $\Omega$ as
the sample space. The space of events $\events$ includes every
possible subset of $\Omega$: it is the powerset~$2^\Omega$. Given the
set of events $\events$, a \emph{probability measure} is a function
$\pmeas : \events \rightarrow [0,1]$ such that:
\begin{itemize}
\item $\pmeas(\Omega) = 1$, and 
\item for a collection $E_{i}$ of pairwise disjoint events, $\pmeas(\bigcup_{i}E_{i})=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\pmeas(E_{i})$,
where $a_{1}\tensor*[_{\mathbb{R}}]{+}{}a_{2}$ and $\tensor*[_{\mathbb{R}}]{\sum}{_{i}}a_{i}$
explicitly specify $a_{i}\in\mathbb{R}$. We may drop the preposing
$\mathbb{R}$ when there is no confusion. 
\end{itemize}

>>>>

The conventional definition of a probability
space~\cite{Kolmogorov1950,rohatgi2011introduction,Swart2013}
builds upon the real numbers. In more detail, a probability space
consists of a \emph{sample space} $\Omega$, a space of
\emph{events}~$\events$, and a \emph{probability measure}~$\pmeas$
mapping events in $\events$ to the real interval $[0,1]$. In this
paper, we will only consider \emph{finite} sets of events: we
therefore restrict our attention to non-empty finite sets $\Omega$ as
the sample space. The space of events $\events$ includes every
possible subset of $\Omega$: it is the powerset~$2^\Omega$. Given the
set of events $\events$, a \emph{probability measure} is a function
$\pmeas : \events \rightarrow [0,1]$ such that:
\begin{itemize}
\item $\pmeas(\Omega) = 1$, and 
\item for a collection $E_{i}$ of pairwise disjoint events, $\pmeas(\bigcup_{i}E_{i})=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\pmeas(E_{i})$,
where $\tensor*[_{\mathbb{R}}]{\sum}{_{i}}a_{i}$
explicitly specify $a_{i}\in\mathbb{R}$. We may drop the preposing
$\mathbb{R}$ when there is no confusion. 
\end{itemize}
